---
format: html
editor_options: 
  chunk_output_type: console
execute:
  warning: false
  message: false
params:
  player: "Tilda Trygger"
  team: "NC State"
---


```{r}
#| echo: false
library(wehoop) # women's basketball data
library(tidyverse)
library(jsonlite) # to read in data from Torvik
library(stringi) # to remove accents from player names
library(hexbin) # for hexagonal shot charts
library(gt)
library(gtExtras)
library(gtUtils)

player_box_scores <- load_wbb_player_box()



# read in USC vs. Washington game on 12-07-25 (for some reason not included in the player box scores)
#usc_vs_uw <- espn_wbb_player_box(401825227)

# read in Notre Dame vs. Ohio State game on 03-23-26 (for some reason not included in the player box scores)
#nd_vs_osu <- espn_wbb_player_box(401856547)

# read in Syracuse vs. UConn game on 03-23-26 (for some reason not included in the player box scores)
#syr_vs_uconn <- espn_wbb_player_box(401856551)

# read in San Francisco vs. Oregon State game on 01-31-26 (for some reason not included in the player box scores)
#sf_vs_ore_st <- espn_wbb_player_box(401828853)

# read in Oregon State vs. Pacific game on 02-14-26 (for some reason not included in the player box scores)
#ore_st_vs_pacific <- espn_wbb_player_box(401828872)

#player_box_scores <- rbind(player_box_scores, usc_vs_uw, nd_vs_osu, syr_vs_uconn, sf_vs_ore_st, ore_st_vs_pacific)

player_stats_total <- player_box_scores |> 
    mutate(across(c(starter, minutes, field_goals_made, field_goals_attempted, three_point_field_goals_made, three_point_field_goals_attempted, free_throws_made, free_throws_attempted, points, rebounds, offensive_rebounds, defensive_rebounds, assists, steals, blocks, turnovers, fouls), ~ replace_na(.x, 0))) |>
  group_by(athlete_id) |> 
  summarize(
    season = last(season),
    team_id = last(team_id),
    athlete_display_name = last(athlete_display_name),
    athlete_jersey = last(athlete_jersey),
    athlete_position_abbreviation = last(athlete_position_abbreviation),
    athlete_position_name = last(athlete_position_name),
    athlete_headshot_href = last(athlete_headshot_href),
    team_display_name = last(team_display_name),
    team_name = last(team_name),
    team_location = last(team_location),
    team_logo = last(team_logo),
    team_abbreviation = last(team_abbreviation),
    team_color = last(team_color),
    team_alternate_color = last(team_alternate_color),
    GP = sum(did_not_play == FALSE),
    GS = sum(starter),
    MIN = sum(minutes),
    FGM = sum(field_goals_made),
    FGA = sum(field_goals_attempted),
    FGM3 = sum(three_point_field_goals_made),
    FGA3 = sum(three_point_field_goals_attempted),
    FTM = sum(free_throws_made),
    FTA = sum(free_throws_attempted),
    PTS = sum(points),
    REB = sum(rebounds),
    OREB = sum(offensive_rebounds),
    DREB = sum(defensive_rebounds),
    AST = sum(assists),
    STL = sum(steals),
    BLK = sum(blocks),
    TO = sum(turnovers),
    FLS = sum(fouls)
  ) |> 
  ungroup()

player_stats_total <- player_stats_total |> 
  filter(MIN > 0) |> 
  mutate(
    MIN_pg = (MIN/GP) |> round(digits = 1),
    FGM_pg = (FGM/GP) |> round(digits = 1),
    FGA_pg = (FGA/GP) |> round(digits = 1),
    FGM3_pg = (FGM3/GP) |> round(digits = 1),
    FGA3_pg = (FGA3/GP) |> round(digits = 1),
    FTM_pg = (FTM/GP) |> round(digits = 1),
    FTA_pg = (FTA/GP) |> round(digits = 1),
    PTS_pg = (PTS/GP) |> round(digits = 1),
    REB_pg = (REB/GP) |> round(digits = 1),
    OREB_pg = (OREB/GP) |> round(digits = 1),
    DREB_pg = (DREB/GP) |> round(digits = 1),
    AST_pg = (AST/GP) |> round(digits = 1),
    STL_pg = (STL/GP) |> round(digits = 1),
    BLK_pg = (BLK/GP) |> round(digits = 1),
    TO_pg = (TO/GP) |> round(digits = 1),
    FLS_pg = (FLS/GP) |> round(digits = 1),
    FG_per = (FGM/FGA) |> round(digits = 3),
    FG3_per = (FGM3/FGA3) |> round(digits = 3),
    FT_per = (FTM/FTA) |> round(digits = 3),
    EFG_per = ((FGM + 0.5*FGM3)/FGA) |> round(digits = 3),
    AST_TO_ratio = (AST/TO) |> round(digits = 3),
    FGM2 = FGM - FGM3,
    FGA2 = FGA - FGA3,
    FGM2_pg = (FGM2/GP) |> round(1),
    FGA2_pg = (FGA2/GP) |> round(1),
    FG2_per = (FGM2/FGA2) |> round(3)
  ) |> 
  mutate(across(c(FG_per, FG3_per, FT_per, EFG_per, AST_TO_ratio), ~ replace_na(.x, 0)))

# create vector of tournament teams
tournament_teams <- c("UConn", "UTSA", "Richmond", "Stephen F. Austin", "Samford", "Arizona State", "Iowa State", "Syracuse", "Maryland", "Murray State", "North Carolina", "Western Illinois", "Notre Dame", "Fairfield", "Ohio State", "Howard", "Illinois", "Colorado", "Vanderbilt", "High Point", "South Carolina", "Southern", "Clemson", "USC", "Michigan State", "Colorado State", "Oklahoma", "Idaho", "Washington", "South Dakota State", "TCU", "UC San Diego", "Georgia", "Virginia", "Iowa", "Fairleigh Dickinson", "UCLA", "California Baptist", "Oklahoma State", "Princeton", "Ole Miss", "Gonzaga", "Minnesota", "Green Bay", "Baylor", "Nebraska", "Duke", "Charleston", "Texas Tech", "Villanova", "LSU", "Jacksonville", "Texas", "Missouri State", "Oregon", "Virginia Tech", "Kentucky", "James Madison", "West Virginia", "Miami (OH)", "Alabama", "Rhode Island", "Louisville", "Vermont", "NC State", "Tennessee", "Michigan", "Holy Cross")

# create player stats in games vs tournament teams
player_stats_vs_tournament <- player_box_scores |> 
  filter(opponent_team_location %in% tournament_teams) |> 
  mutate(across(c(starter, minutes, field_goals_made, field_goals_attempted, three_point_field_goals_made, three_point_field_goals_attempted, free_throws_made, free_throws_attempted, points, rebounds, offensive_rebounds, defensive_rebounds, assists, steals, blocks, turnovers, fouls), ~ replace_na(.x, 0))) |>
  group_by(athlete_id) |> 
  summarize(
    season = last(season),
    team_id = last(team_id),
    athlete_display_name = last(athlete_display_name),
    athlete_jersey = last(athlete_jersey),
    athlete_position_abbreviation = last(athlete_position_abbreviation),
    athlete_position_name = last(athlete_position_name),
    athlete_headshot_href = last(athlete_headshot_href),
    team_display_name = last(team_display_name),
    team_name = last(team_name),
    team_location = last(team_location),
    team_logo = last(team_logo),
    team_abbreviation = last(team_abbreviation),
    team_color = last(team_color),
    team_alternate_color = last(team_alternate_color),
    GP = sum(minutes > 0),
    GS = sum(starter),
    MIN = sum(minutes),
    FGM = sum(field_goals_made),
    FGA = sum(field_goals_attempted),
    FGM3 = sum(three_point_field_goals_made),
    FGA3 = sum(three_point_field_goals_attempted),
    FTM = sum(free_throws_made),
    FTA = sum(free_throws_attempted),
    PTS = sum(points),
    REB = sum(rebounds),
    OREB = sum(offensive_rebounds),
    DREB = sum(defensive_rebounds),
    AST = sum(assists),
    STL = sum(steals),
    BLK = sum(blocks),
    TO = sum(turnovers),
    FLS = sum(fouls)
  ) |> 
  ungroup()

player_stats_vs_tournament <- player_stats_vs_tournament |> 
  filter(MIN > 0) |> 
  mutate(
    MIN_pg = (MIN/GP) |> round(digits = 1),
    FGM_pg = (FGM/GP) |> round(digits = 1),
    FGA_pg = (FGA/GP) |> round(digits = 1),
    FGM3_pg = (FGM3/GP) |> round(digits = 1),
    FGA3_pg = (FGA3/GP) |> round(digits = 1),
    FTM_pg = (FTM/GP) |> round(digits = 1),
    FTA_pg = (FTA/GP) |> round(digits = 1),
    PTS_pg = (PTS/GP) |> round(digits = 1),
    REB_pg = (REB/GP) |> round(digits = 1),
    OREB_pg = (OREB/GP) |> round(digits = 1),
    DREB_pg = (DREB/GP) |> round(digits = 1),
    AST_pg = (AST/GP) |> round(digits = 1),
    STL_pg = (STL/GP) |> round(digits = 1),
    BLK_pg = (BLK/GP) |> round(digits = 1),
    TO_pg = (TO/GP) |> round(digits = 1),
    FLS_pg = (FLS/GP) |> round(digits = 1),
    FG_per = (FGM/FGA) |> round(digits = 3),
    FG3_per = (FGM3/FGA3) |> round(digits = 3),
    FT_per = (FTM/FTA) |> round(digits = 3),
    EFG_per = ((FGM + 0.5*FGM3)/FGA) |> round(digits = 3),
    AST_TO_ratio = (AST/TO) |> round(digits = 3),
    FGM2 = FGM - FGM3,
    FGA2 = FGA - FGA3,
    FGM2_pg = (FGM2/GP) |> round(1),
    FGA2_pg = (FGA2/GP) |> round(1),
    FG2_per = (FGM2/FGA2) |> round(3)
  ) |> 
  mutate(across(c(FG_per, FG3_per, FT_per, EFG_per, AST_TO_ratio), ~ replace_na(.x, 0)))

# save women's advanceed players stats from barttovrik.com (in JSON format) as a url and read them in
json_file <- "https://barttorvik.com/ncaaw/getadvstats.php?year=2026"
json_data <- jsonlite::fromJSON(json_file, flatten = TRUE)

# convert the data to a tibble
json_tibble <- as_tibble(json_data)

# get Torvik data just for players vs top 100 opponents
json_file_top_100 <- "https://barttorvik.com/ncaaw/pslice.php?year=2026&top=100"
json_data_top_100 <- jsonlite::fromJSON(json_file_top_100, flatten = TRUE)

# convert the data to a tibble
json_tibble_top_100 <- as_tibble(json_data_top_100)

# rename the variables
torvik_player_tibble <- json_tibble |> 
  rename(
  "player_name" = "V1",
  "team" = "V2",
  "conference" = "V3",
  "games_played" = "V4",
  "min_percent" = "V5",
  "off_rtg" = "V6",
  "usage" = "V7",
  "efg_per" = "V8",
  "ts_per" = "V9",
  "or_per" = "V10",
  "dr_per" = "V11",
  "ast_per" = "V12",
  "to_per" = "V13",
  "ft_made" = "V14",
  "ft_att" = "V15",
  "ft_per" = "V16",
  "fgm2" = "V17",
  "fga2" = "V18",
  "fg2_per" = "V19",
  "fgm3" = "V20",
  "fga3" = "V21",
  "fg3_per" = "V22",
  "blk_per" = "V23",
  "stl_per" = "V24",
  "ft_rate" = "V25",
  "class" = "V26",
  "height" = "V27",
  "jersey" = "V28",
  "porpagatu" = "V29",
  "adj_oe" = "V30",
  "fouls_per_40" = "V31",
  "season" = "V32",
  "player_id" = "V33",
  "hometown" = "V34",
  "recruiT_rank" = "V35",
  "ast_to_ratio" = "V36",
  "rim_fgm" = "V37",
  "rim_fga" = "V38",
  "non_rim2_fgm" = "V39",
  "non_rim2_fga" = "V40",
  "rim_fg_per" = "V41",
  "non_rim2_fg_per" = "V42",
  "dunk_fgm" = "V43",
  "dunk_fga" = "V44",
  
  
  "def_rtg_unadjusted" = "V47",
  "def_rtg" = "V48",
  "d_porpagatu" = "V49",
  "stops_maybe" = "V50",
  "old_BPM_torvik" = "V51",
  "old_OBPM_torvik" = "V52",
  "old_DBPM_torvik" = "V53",
  "BPM_torvik" = "V54",
  "min_pg" = "V55",
  "OBPM_torvik" = "V56",
  "DBPM_torvik" = "V57",
  "or_pg" = "V58",
  "dr_pg" = "V59",
  "reb_pg" = "V60",
  "ast_pg" = "V61",
  "stl_pg" = "V62",
  "blk_pg" = "V63",
  "pts_pg" = "V64",
  "role" = "V65",
  "fga3_per_100_poss" = "V66"
) |> 
  mutate(
    across(c(4:25, 29:32, 35:64, 66), as.numeric),
    total_prpg = porpagatu + d_porpagatu,
    fga = fga2 + fga3,
    fgm = fgm2 + fgm3,
    fg_per = (fgm/fga) |> round(3)
  ) |> 
  select(-c(V45, V46))

torvik_player_tibble <- torvik_player_tibble |> 
  mutate(
    team = ifelse(team |> str_ends("St."), str_replace_all(team, "St.", "State"), team)
  )

# rename the variables for vs top 100 opponents
torvik_players_vs_top_100 <- json_tibble_top_100 |> 
  rename(
  "player_name" = "V1",
  "team" = "V2",
  "conference" = "V3",
  "games_played" = "V4",
  "min_percent" = "V5",
  "off_rtg" = "V6",
  "usage" = "V7",
  "efg_per" = "V8",
  "ts_per" = "V9",
  "or_per" = "V10",
  "dr_per" = "V11",
  "ast_per" = "V12",
  "to_per" = "V13",
  "ft_made" = "V14",
  "ft_att" = "V15",
  "ft_per" = "V16",
  "fgm2" = "V17",
  "fga2" = "V18",
  "fg2_per" = "V19",
  "fgm3" = "V20",
  "fga3" = "V21",
  "fg3_per" = "V22",
  "blk_per" = "V23",
  "stl_per" = "V24",
  "ft_rate" = "V25",
  "class" = "V26",
  "height" = "V27",
  "jersey" = "V28",
  "porpagatu" = "V29",
  "adj_oe" = "V30",
  "fouls_per_40" = "V31",
  "season" = "V32",
  "player_id" = "V33",
  
  "recruiT_rank" = "V35",
  "ast_to_ratio" = "V36",
  "rim_fgm" = "V37",
  "rim_fga" = "V38",
  "non_rim2_fgm" = "V39",
  "non_rim2_fga" = "V40",
  "rim_fg_per" = "V41",
  "non_rim2_fg_per" = "V42",
  "dunk_fgm" = "V43",
  "dunk_fga" = "V44",
  
  
  "def_rtg_unadjusted" = "V47",
  "def_rtg" = "V48",
  "d_porpagatu" = "V49",
  "stops_maybe" = "V50",
  "old_BPM_torvik" = "V51",
  "old_OBPM_torvik" = "V52",
  "old_DBPM_torvik" = "V53",
  "BPM_torvik" = "V54",
  "min_pg" = "V55",
  "OBPM_torvik" = "V56",
  "DBPM_torvik" = "V57",
  "or_pg" = "V58",
  "dr_pg" = "V59",
  "reb_pg" = "V60",
  "ast_pg" = "V61",
  "stl_pg" = "V62",
  "blk_pg" = "V63",
  "pts_pg" = "V64",
  "role" = "V65",
  "fga3_per_100_poss" = "V66"
) |> 
  mutate(
    across(c(4:25, 29:32, 35:64, 66), as.numeric),
    total_prpg = porpagatu + d_porpagatu,
    fga = fga2 + fga3,
    fgm = fgm2 + fgm3,
    fg_per = (fgm/fga) |> round(3)
  ) |> 
  select(-c(V45, V46))

torvik_players_vs_top_100 <- torvik_players_vs_top_100 |> 
  mutate(
    team = ifelse(team |> str_ends("St."), str_replace_all(team, "St.", "State"), team)
  )

# define differences in team names between ESPN and Torvik
team_aliases_torvik <- tribble(
  ~torvik_name,                           ~espn_name,
  "Cal St. Northridge",                   "Cal State Northridge",
  "Cal St. Fullerton",                    "Cal State Fullerton",
  "Cal St. Bakersfield",                  "Cal State Bakersfield",
  "UMKC",                                 "Kansas City",
  "Nicholls State",                       "Nicholls",
  "McNeese State",                        "McNeese",
  "N.C. State",                           "NC State",
  "Arkansas Pine Bluff",                  "Arkansas-Pine Bluff",
  "Albany",                               "UAlbany",
  "Bethune Cookman",                      "Bethune-Cookman",
  "Texas A&M Corpus Chris",             "Texas A&M-Corpus Christi",
  "Mississippi",                          "Ole Miss",
  "Connecticut",                          "UConn",
  "Gardner Webb",                         "Gardner-Webb",
  "Grambling State",                      "Grambling",
  "Hawaii",                               "Hawai'i",
  "Illinois Chicago",                     "UIC",
  "LIU",                                  "Long Island University",
  "Louisiana Monroe",                     "UL Monroe",
  "Miami FL",                             "Miami",
  "Nebraska Omaha",                       "Omaha",
  "USC Upstate",                          "South Carolina Upstate",
  "Southeastern Louisiana",               "SE Louisiana",
  "Southeast Missouri",                   "Southeast Missouri State",
  "Stephen F Austin",                     "Stephen F. Austin",
  "Sam Houston State",                    "Sam Houston",
  "San Jose State",                       "San José State",
  "Seattle",                              "Seattle U",
  "Tennessee Martin",                     "UT Martin",
  "American",                             "American University",
  "Appalachian State",                    "App State",
  "Cal Baptist",                          "California Baptist",
  "FIU",                                  "Florida International",
  "IU Indy",                              "IU Indianapolis",
  "Loyola MD",                            "Loyola Maryland",
  "Miami OH",                             "Miami (OH)",
  "Penn",                                 "Pennsylvania",
  "Queens",                               "Queens University",
  "St. Thomas",                           "St. Thomas-Minnesota"
)

# clean the team names for the Torvik data
torvik_player_tibble <- torvik_player_tibble |>
  left_join(team_aliases_torvik, by = c("team" = "torvik_name")) |>
  mutate(team = coalesce(espn_name, team)) |>
  select(-espn_name)

torvik_players_vs_top_100 <- torvik_players_vs_top_100 |>
  left_join(team_aliases_torvik, by = c("team" = "torvik_name")) |>
  mutate(team = coalesce(espn_name, team)) |>
  select(-espn_name)

d1_teams <- as.vector(torvik_player_tibble$team)

player_stats_total <- player_stats_total |> 
  filter(team_location %in% d1_teams)

player_stats_vs_tournament <- player_stats_vs_tournament |> 
  filter(team_location %in% d1_teams)

# save the player names in a tibble with the IDs to merge back 
save_player_names <- player_stats_total |> 
  select(athlete_id, athlete_display_name)

save_player_names_vs_good_teams <- player_stats_vs_tournament |> 
  select(athlete_id, athlete_display_name)

# remove apostrophes, hyphens, and accents from player names in the data from ESPN
player_stats_total <- player_stats_total |> 
  mutate(
    athlete_display_name = athlete_display_name |>
      str_remove_all("[-']") |>
      stri_trans_general("Latin-ASCII")
  )

player_stats_vs_tournament <- player_stats_vs_tournament |> 
  mutate(
    athlete_display_name = athlete_display_name |>
      str_remove_all("[-']") |>
      stri_trans_general("Latin-ASCII")
  )

# remove apostrophes, hyphens, and accents from player names in the Torvik data
torvik_player_tibble <- torvik_player_tibble |> 
  mutate(
    player_name = player_name |>
      str_remove_all("[-']") |>
      stri_trans_general("Latin-ASCII")
  )

torvik_players_vs_top_100 <- torvik_players_vs_top_100 |> 
  mutate(
    player_name = player_name |>
      str_remove_all("[-']") |>
      stri_trans_general("Latin-ASCII")
  )

# combine box score stats with stats from Torvik
player_stats_total <- player_stats_total |> 
  left_join(torvik_player_tibble, by = c("team_location" = "team",
                                         "athlete_display_name" = "player_name",
                                         "season" = "season",
                                         "athlete_jersey" = "jersey")) 

# convert athlete_display_name to "player"
player_stats_total <- player_stats_total |> 
  rename("player" = "athlete_display_name")

# go back to original player names
player_stats_total <- save_player_names |> 
  left_join(player_stats_total, by = c("athlete_id")) |> 
  select(-player)

# combine box score stats with stats from Torvik for good teams
player_stats_vs_tournament <- player_stats_vs_tournament |> 
  left_join(torvik_players_vs_top_100, by = c("team_location" = "team",
                                         "athlete_display_name" = "player_name",
                                         "season" = "season",
                                         "athlete_jersey" = "jersey")) 

# convert athlete_display_name to "player"
player_stats_vs_tournament <- player_stats_vs_tournament |> 
  rename("player" = "athlete_display_name")

# go back to original player names
player_stats_vs_tournament <- save_player_names_vs_good_teams |> 
  left_join(player_stats_vs_tournament, by = c("athlete_id")) |> 
  select(-player)

# create variable of a player's class for the upcoming 2027
player_stats_total <- player_stats_total |> 
  mutate(
    class2027 = case_when(
      class == "Fr" ~ "Sophomore",
      class == "So" ~ "Junior",
      class == "Jr" ~ "Senior",
      class == "Sr" ~ "Grad/Done",
      class == "--" | is.na(class) ~ "--"
    )
  )

# set a team's color to black if they do not have one
player_stats_total <- player_stats_total |> 
  mutate(
    team_color = ifelse(is.na(team_color), "000000", team_color)
  )

# set a team's alternate color to white if they do not have one
player_stats_total <- player_stats_total |> 
  mutate(
    team_alternate_color = ifelse(is.na(team_alternate_color), "ffffff", team_alternate_color)
  )
```


```{r}
#| echo: false
# hexagonal shot charts
# load NCAA women's basketball play-by-play data
wbb_pbp <- wehoop::load_wbb_pbp()

# add player names and headshots to play-by-play data
wbb_pbp <- wbb_pbp |> 
  left_join(player_box_scores, by = c("athlete_id_1" = "athlete_id", 
                                      "team_id" = "team_id",
                                      "season" = "season",
                                      "season_type" = "season_type",
                                      "game_id" = "game_id",
                                      "game_date" = "game_date",
                                      "game_date_time" = "game_date_time"))

# get just shoooting plays from the play-by-play data and adjust their coordinates
wbb_shots <- wbb_pbp |> 
  filter(
    shooting_play == TRUE, 
    !(type_text %in% c("MadeFreeThrow", "MissedFreeThrow"))
  ) |> 
  mutate(
    loc_x = -1*(coordinate_x_raw - 25),
    loc_y = coordinate_y_raw + 5
   ) |> 
  dplyr::select(
    team_location,
    athlete_display_name,
    text,
    loc_x,
    loc_y,
    scoring_play,
    team_logo,
    athlete_jersey,
    athlete_headshot_href,
    athlete_position_name,
    athlete_position_abbreviation,
    athlete_id_1,
    team_id,
    team_name,
    team_abbreviation,
    team_slug,
    team_color,
    opponent_team_location,
    game_date
  )

wbb_shots <- wbb_shots |>
  mutate(
    shot_distance = sqrt(loc_x^2 + loc_y^2) - 5.25,
    shot_zone_range = case_when(
      shot_distance <= 4 ~ "Restricted Area",
      shot_distance <= 8 ~ "In The Paint (Non-RA)",
      shot_distance <= 16 ~ "Mid-Range",
      shot_distance <= 22.1458 ~ "Mid-Range",
      TRUE ~ "3PT"
    ),
    shot_zone_area = case_when(
      loc_x < -8 ~ "Left Side",
      loc_x >  8 ~ "Right Side",
      TRUE       ~ "Center"
    ),
    shot_zone_area = case_when(
      shot_zone_range == "3PT" & abs(loc_x) > 22 ~ "Corner",
      TRUE ~ shot_zone_area
    ),
    shot_made_numeric = as.integer(scoring_play),
    shot_value = case_when(
      grepl("three", text) ~ 3L,
      grepl("Three", text) ~ 3L,
      TRUE                 ~ 2L
    )
  )

# get national averages in FG% from different shot zones
averages <- wbb_shots |> 
  group_by(
    shot_zone_range, 
    shot_zone_area
    ) |> 
  summarize(
    fgm = sum(shot_made_numeric),
    fga = n(),
    league_pct = fgm/fga,
    .groups = "drop"
  )

# create the court points
##Draw court (from https://raw.githubusercontent.com/Henryjean/NBA-Court/refs/heads/main/CourtDimensions.R) (dimensions changed from NBA to college)
width = 50
height = 94/2
key_height = 19
inner_key_width = 12
outer_key_width = 12 #Edited to same as inner key, as no outer key in college
backboard_width = 6
backboard_offset = 4
neck_length = 0.5
hoop_radius = 0.75
hoop_center_y = backboard_offset + neck_length + hoop_radius
three_point_radius = 22.1458333 #Edited to college 3 point line
three_point_side_radius = 21.65625 #Edited to college 3 point line
three_point_side_height = 9.86458333 #Edited to college 3 point line

circle_points = function(center = c(0, 0), radius = 1, npoints = 360) {
  angles = seq(0, 2 * pi, length.out = npoints)
  return(data.frame(x = center[1] + radius * cos(angles),
                    y = center[2] + radius * sin(angles)))
}

court_points = data.frame(
  x = c(width / 2, width / 2, -width / 2, -width / 2, width / 2, 
        outer_key_width / 2, outer_key_width / 2, -outer_key_width / 2, -outer_key_width / 2,
        -backboard_width / 2, backboard_width / 2, 
        0, 0),
  y = c(height, 0, 0, height, height, 0, key_height, key_height, 0,
        backboard_offset, backboard_offset, 
        backboard_offset, backboard_offset + neck_length),
  desc = c(rep("perimeter", 5), rep("outer_key", 4), rep("backboard", 2),
           rep("neck", 2))
)

# define foul circle
foul_circle = circle_points(center = c(0, key_height), radius = inner_key_width / 2)
foul_circle_top = filter(foul_circle, y > key_height) %>% mutate(desc = "foul_circle_top")
foul_circle_bottom = filter(foul_circle, y < key_height) %>% mutate(desc = "foul_circle_bottom") #Not included in this chart as no bottom ft circle in college

# define hoop
hoop = circle_points(center = c(0, hoop_center_y), radius = hoop_radius) %>% mutate(desc = "hoop") 
restricted = circle_points(center = c(0, hoop_center_y), radius = 4) %>%
  filter(y >= hoop_center_y) %>%
  mutate(desc = "restricted")

# define 3-point line
three_point_circle = circle_points(center = c(0, hoop_center_y), radius = three_point_radius) %>% filter(y >= three_point_side_height)
three_point_line = data.frame(
  x = c(three_point_side_radius, three_point_side_radius, three_point_circle$x, -three_point_side_radius, -three_point_side_radius),
  y = c(0, three_point_side_height, three_point_circle$y, three_point_side_height, 0),
  desc = "three_point_line"
)

# combine all court points into one object that can be used
court_points = rbind(court_points , foul_circle_top, hoop, restricted, three_point_line)

# altered ggplot theme from the F5
theme_f5 <- function (font_size = 9) { 
  theme_minimal(base_size = font_size, base_family = "roboto") %+replace% 
    theme(
      plot.background = element_rect(fill = 'floralwhite', color = "floralwhite"), 
      panel.grid.minor = element_blank(), 
      plot.title = element_text(hjust = 0, size = 14, face = 'bold'), 
      plot.subtitle = element_text(color = 'gray65', hjust = 0, margin=margin(2.5,0,10,0), size = 9), 
      plot.caption = element_text(color = 'gray65', margin=margin(-2,0,0,0), hjust = 1, size = 6)
    )
}


# below functions used for hexagonal charts
hex_bounds <- function(x, binwidth) {
  c(
    plyr::round_any(min(x), binwidth, floor) - 1e-6,
    plyr::round_any(max(x), binwidth, ceiling) + 1e-6
  )
}

calculate_hex_coords = function(shots, binwidths) {
  xbnds = hex_bounds(shots$loc_x, binwidths[1])
  xbins = diff(xbnds) / binwidths[1]
  ybnds = hex_bounds(shots$loc_y, binwidths[2])
  ybins = diff(ybnds) / binwidths[2]
  
  hb = hexbin(
    x = shots$loc_x,
    y = shots$loc_y,
    xbins = xbins,
    xbnds = xbnds,
    ybnds = ybnds,
    shape = ybins / xbins,
    IDs = TRUE
  )
  
  shots = mutate(shots, hexbin_id = hb@cID)
  
  hexbin_stats = shots  |> 
    group_by(hexbin_id) |>
    summarize(
      hex_attempts = n(),
      hex_pct = mean(shot_made_numeric),
      hex_points_scored = sum(shot_made_numeric * shot_value),
      hex_points_per_shot = mean(shot_made_numeric * shot_value),
      .groups = "drop"
    )
  
  hexbin_ids_to_zones = shots |>
    dplyr::group_by(hexbin_id, shot_zone_range, shot_zone_area) |>
    summarize(attempts = n(), .groups = "drop") |>
    arrange(hexbin_id, desc(attempts)) |>
    group_by(hexbin_id) |>
    filter(row_number() == 1) |>
    select(hexbin_id, shot_zone_range, shot_zone_area)
  
  hexbin_stats = inner_join(hexbin_stats, hexbin_ids_to_zones, by = "hexbin_id")
  
  # from hexbin package, see: https://github.com/edzer/hexbin
  sx = hb@xbins / diff(hb@xbnds)
  sy = (hb@xbins * hb@shape) / diff(hb@ybnds)
  dx = 1 / (2 * sx)
  dy = 1 / (2 * sqrt(3) * sy)
  origin_coords = hexcoords(dx, dy)
  
  hex_centers = hcell2xy(hb)
  
  hexbin_coords = bind_rows(lapply(1:hb@ncells, function(i) {
    tibble(
      x = origin_coords$x + hex_centers$x[i],
      y = origin_coords$y + hex_centers$y[i],
      center_x = hex_centers$x[i],
      center_y = hex_centers$y[i],
      hexbin_id = hb@cell[i]
    )
  }))
  
  inner_join(hexbin_coords, hexbin_stats, by = "hexbin_id")
}

# min_radius_factor controls the difference in sizes between hex bins
# binwidths control the overall size of the bins
calculate_hexbins_from_shots = function(shots, league_averages = averages, binwidths = c(2.5, 2.5), min_radius_factor = 0.4, fg_diff_limits = c(-0.12, 0.12), fg_pct_limits = c(0.2, 0.7), pps_limits = c(0.5, 1.5)) {
  shots <- tibble::as_tibble(as.data.frame(shots))
  league_averages <- tibble::as_tibble(as.data.frame(league_averages))
  
  if (nrow(shots) == 0) {
    return(list())
  }
  
  grouped_shots = shots |> 
    group_by(shot_zone_range, shot_zone_area)
  
  zone_stats = grouped_shots |>
    summarize(
      zone_attempts = n(),
      zone_pct = mean(shot_made_numeric),
      zone_points_scored = sum(shot_made_numeric * shot_value),
      zone_points_per_shot = mean(shot_made_numeric * shot_value),
      .groups = "drop"
    )
  
  league_zone_stats = league_averages |>
    group_by(shot_zone_range, shot_zone_area) |>
    summarize(league_pct = sum(fgm) / sum(fga), .groups = "drop")
  
  hex_data = calculate_hex_coords(shots, binwidths = binwidths)
  
  join_keys = c("shot_zone_area", "shot_zone_range")
  
  hex_data = hex_data |>
    inner_join(zone_stats, by = join_keys) |>
    inner_join(league_zone_stats, by = join_keys)
  
  max_hex_attempts = max(hex_data$hex_attempts)
  
  hex_data = mutate(hex_data,
                    radius_factor = min_radius_factor + (1 - min_radius_factor) * log(hex_attempts + 1) / log(max_hex_attempts + 1),
                    adj_x = center_x + radius_factor * (x - center_x),
                    adj_y = center_y + radius_factor * (y - center_y),
                    bounded_fg_diff = pmin(pmax(zone_pct - league_pct, fg_diff_limits[1]), fg_diff_limits[2]),
                    bounded_fg_pct = pmin(pmax(zone_pct, fg_pct_limits[1]), fg_pct_limits[2]),
                    bounded_points_per_shot = pmin(pmax(zone_points_per_shot, pps_limits[1]), pps_limits[2]))
  
  list(
    hex_data = hex_data, 
    fg_diff_limits = fg_diff_limits, 
    fg_pct_limits = fg_pct_limits, 
    pps_limits = pps_limits, 
    player_name = shots$athlete_display_name[1], 
    team_name = shots$team_location[1], 
    player_number = shots$athlete_jersey[1], 
    player_headshot = shots$athlete_headshot_href[1], 
    player_position = shots$athlete_position_name[1],
    fgm = shots |> filter((grepl("made", text) | grepl("makes", text))) |> nrow(),
    fga = nrow(shots),
    fgm3 = shots |> filter((grepl("Three", text) | grepl("three", text)) & (grepl("made", text) | grepl("makes", text))) |> nrow(),
    fga3 = shots |> filter(grepl("Three", text) | grepl("three", text)) |> nrow()
       )
}


percent_formatter = function(x) {
  scales::percent(x, accuracy = 1)
}

points_formatter = function(x) {
  scales::comma(x, accuracy = 0.01)
}

# function to create the hexagonal shot charts from hexagonal shot data
generate_hex_chart = function(hex_data, base_court = court_points, metric = "bounded_fg_diff", alpha_range = c(0.85, 0.98)) {
  if (length(hex_data) == 0) {
    return(base_court)
  }
  
  if (metric == "bounded_fg_diff") {
    fill_limit = hex_data$fg_diff_limits
    fill_label = "FG% vs. National Avg"
    label_formatter = percent_formatter
  } else if (metric == "bounded_fg_pct") {
    fill_limit = hex_data$fg_pct_limits
    fill_label = "FG%"
    label_formatter = percent_formatter
  } else if (metric == "bounded_points_per_shot") {
    fill_limit = hex_data$pps_limits
    fill_label = "Points Per Shot"
    label_formatter = points_formatter
  } else {
    stop("invalid metric")
  }
  
  ggplot() + 
  geom_path(data = court_points,
            aes(x = x, y = y, group = desc),
            color = "black", linewidth = .4,
            , inherit.aes = FALSE) +
    geom_polygon(
      data = hex_data$hex_data,
      aes(
        x = adj_x,
        y = adj_y,
        group = hexbin_id,
        fill = !!sym(metric),
        alpha = hex_attempts
      ),
      # size = court_theme$hex_border_size,
      # color = court_theme$hex_border_color
    ) +
    # custom theme
    theme_f5()  +
    # set opacity limits
    #scale_alpha_continuous(range = c(0.4, 1)) +
    # set y-axis limits
    scale_y_continuous(limits = c(-2.5, 45), oob = scales::oob_squish) +
    # set x-axis limits
    scale_x_continuous(limits = c(-30, 30), oob = scales::oob_squish) + 
    # theme tweaks
    theme(line = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(), 
          plot.margin = margin(.25, 0, 0.25, 0, "lines"),
          plot.title = element_text(face = 'bold', hjust= .5, vjust = 0, family = "roboto", size = 25),
          plot.subtitle = element_text(face = 'bold', hjust= .5, vjust = 0, family = "roboto", size = 15, lineheight = 0.25),
          plot.caption = element_text(size = 20)) + 
    scale_fill_viridis_c(
      paste0(fill_label, "   "),
      limit = fill_limit,
      labels = label_formatter
    ) +
    scale_alpha_continuous(guide = FALSE, range = alpha_range, trans = "sqrt") +
    theme(legend.text = element_text(size = rel(4)), 
      legend.title = element_text(size = rel(6))) + 
    guides(
      fill = guide_colourbar(position = "bottom", barwidth = 24, barheight = 6)
    ) + 
    # labs(
    #   title = ifelse(!is.na(hex_data$player_headshot),
    #                  paste0("<img src = '", hex_data$player_headshot, "' height = 50>",
    #                         "<span style='font-size: 40pt'>",
    #                         hex_data$player_name,
    #                         " Hex Chart</span>"),
    #                  paste0(hex_data$player_name, " Hex Chart")
    #   ),
    #   subtitle = paste0("#", hex_data$player_number, ", ", hex_data$player_position)
    #   ) + 
      annotate("label",
               x = 17, y = 41,
               label = paste0("FG: ", hex_data$fgm, "/", hex_data$fga, " \n 3 FG: ", hex_data$fgm3, "/", hex_data$fga3),
               size = 14,
               color = "black",
               fill = "floralwhite",
               fontface = "bold",
               lineheight = 1, # Controls line spacing (default is 1)
               label.padding = unit(0.2, "lines"),  # Reduces padding inside the label (less space between text and label border)
               linewidth = 2  # increase border thickness
      ) #+
    # theme(
    #   plot.title = ggtext::element_markdown()
    # )
}

# create function to automatically plot hex charts (don't have to worry about having to generate hex data and then hex chart, all in one step with this)
plot_hex_chart <- function(player = "Tilda Trygger", team = "NC State"){
  
  # filter to only get the player shots desired
  player_shots <- wbb_shots |> 
  filter(
    athlete_display_name == player,
    team_location == team
  )
  
  # generate hex data for the player
  player_hex_data <- calculate_hexbins_from_shots(shots = player_shots)
  
  # plot the hexagonal shot chart
  generate_hex_chart(hex_data = player_hex_data)
}
```

```{r}
#| echo: false
headshot_url <- player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  pull(athlete_headshot_href)

team_logo_url <- player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  pull(team_logo)

team_color <- player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  pull(team_color)

team_alternate_color <- player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  pull(team_alternate_color)
```

:::: {.columns}
::: {.column width="38%"}
```{=html}
<div style="position: relative; display: inline-block; width: 300px;">
  <img src="`r headshot_url`" width="300"/>
  <div style="position: absolute; bottom: -42px; right: 5px;
              width: 80px; height: 80px;
              background-color: #`r team_alternate_color`;
              border-radius: 50%;
              border: 2px solid #`r team_color`;">
    <img src="`r team_logo_url`" width="65"
         style="display: block; margin: auto; padding-top: 6px;"/>
  </div>
</div>
```
:::
::: {.column width="27%"}
**Player: **`{r} player_stats_total |> 
  filter(
  athlete_display_name == params$player,
    team_location == params$team
) |> 
  pull(athlete_display_name)`

**Team: **`{r} player_stats_total |> 
  filter(athlete_display_name == params$player,
    team_location == params$team) |> 
  pull(team_location)`
  
**Role: **`{r} player_stats_total |> 
  filter(athlete_display_name == params$player,
    team_location == params$team) |> 
  pull(role)`
  
**Height: **`{r} player_stats_total |> 
  filter(athlete_display_name == params$player,
    team_location == params$team) |> 
  pull(height)`
  

**Class in 2027: **`{r} player_stats_total |> 
  filter(athlete_display_name == params$player,
    team_location == params$team) |> 
  pull(class2027)`
  
**Hometown: **`{r} player_stats_total |> 
  filter(athlete_display_name == params$player,
    team_location == params$team) |> 
  pull(hometown)`
:::
::: {.column width="35%"}
```{r}
#| echo: false
#| fig-width: 18
#| fig-height: 16
plot_hex_chart(player = params$player, team = params$team)
```
:::
::::

## Player Stats (`{r} player_stats_total |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(GP)` Games)
```{r}
#| echo: false
player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  select(
    MIN_pg, PTS_pg, REB_pg, OREB_pg, DREB_pg, AST_pg, BLK_pg, STL_pg, TO_pg, FG_per, FG3_per, FT_per
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    MIN_pg = "MIN",
    PTS_pg = "PTS",
    OREB_pg = "OREB",
    DREB_pg = "DREB",
    AST_pg = "AST",
    BLK_pg = "BLK",
    FG_per = "FG%", 
    FG3_per = "3FG%",
    REB_pg = "TREB",
    FT_per = "FT%",
    STL_pg = "STL",
    TO_pg = "TO"
  ) |> 
  gt_theme_ncaa()
```

## Player Stats vs. Tournament Teams (`{r} player_stats_vs_tournament |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(GP)` Games)
```{r}
#| echo: false
player_stats_vs_tournament |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  select(
    MIN_pg, PTS_pg, REB_pg, OREB_pg, DREB_pg, AST_pg, BLK_pg, STL_pg, TO_pg, FG_per, FG3_per, FT_per
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    MIN_pg = "MIN",
    PTS_pg = "PTS",
    OREB_pg = "OREB",
    DREB_pg = "DREB",
    AST_pg = "AST",
    BLK_pg = "BLK",
    FG_per = "FG%", 
    FG3_per = "3FG%", 
    REB_pg = "TREB",
    FT_per = "FT%",
    STL_pg = "STL",
    TO_pg = "TO"
  ) |> 
  gt_theme_ncaa()
```

## Shooting Splits (`{r} player_stats_total |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(GP)` Games)
```{r}
#| echo: false
player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  select(
    FGM, FGA, FG_per, FGM2, FGA2, FG2_per, FGM3, FGA3, FG3_per, FTM, FTA, FT_per, EFG_per
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    FGM = "FG",
    FGA = "FGA",
    FG_per = "FG%", 
    FGM2 = "FG2",
    FGA2 = "FGA2",
    FG2_per = "FG2%",
    FGM3 = "3FG",
    FGA3 = "3FGA",
    FG3_per = "3FG%", 
    FTM = "FT",
    FTA = "FTA",
    FT_per = "FT%",
    EFG_per = "EFG%"
  ) |> 
  gt_theme_ncaa()

player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  mutate(
    rim_fg_per = rim_fg_per |> round(3),
    non_rim2_fg_per = non_rim2_fg_per |> round(3)
  ) |> 
  select(
    rim_fgm, rim_fga, rim_fg_per, non_rim2_fgm, non_rim2_fga, non_rim2_fg_per
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    rim_fgm = "Short 2 FG",
    rim_fga = "Short 2 FGA",
    rim_fg_per = "Short 2 FG%",
    non_rim2_fgm = "Long 2 FG",
    non_rim2_fga = "Long 2 FGA",
    non_rim2_fg_per = "Long 2 FG%"
  ) |> 
  gt_theme_ncaa()
```

## Shooting Splits vs. Tournament Teams (`{r} player_stats_vs_tournament |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(GP)` Games)
```{r}
#| echo: false
player_stats_vs_tournament |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  select(
    FGM, FGA, FG_per, FGM2, FGA2, FG2_per, FGM3, FGA3, FG3_per, FTM, FTA, FT_per, EFG_per
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    FGM = "FG",
    FGA = "FGA",
    FG_per = "FG%", 
    FGM2 = "FG2",
    FGA2 = "FGA2",
    FG2_per = "FG2%",
    FGM3 = "3FG",
    FGA3 = "3FGA",
    FG3_per = "3FG%", 
    FTM = "FT",
    FTA = "FTA",
    FT_per = "FT%",
    EFG_per = "EFG%"
  ) |> 
  gt_theme_ncaa()
```

## Advanced Stats (`{r} player_stats_total |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(GP)` Games)
```{r}
#| echo: false
player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  mutate(
    TS_per = (ts_per/100) |> round(digits = 3)
  ) |> 
  select(
    usage, 
    AST_TO_ratio,
    EFG_per,
    TS_per,
    dr_per,
    or_per,
    stl_per,
    blk_per,
    to_per,
    fouls_per_40
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    usage = "Usage", 
    AST_TO_ratio = "AST/TO",
    EFG_per = "EFG%",
    TS_per = "TS%",
    dr_per = "DREB%",
    or_per = "OREB%",
    stl_per = "STL%",
    blk_per = "BLK%",
    to_per = "TO%",
    fouls_per_40 = "Fouls/40"
  ) |> 
  gt_theme_ncaa()
```

## Advanced Stats vs Top 100 Teams (`{r} player_stats_vs_tournament |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(games_played)` Games)
```{r}
#| echo: false
player_stats_vs_tournament |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  mutate(
    TS_per = (ts_per/100) |> round(digits = 3)
  ) |> 
  select(
    usage, 
    AST_TO_ratio,
    EFG_per,
    TS_per,
    dr_per,
    or_per,
    stl_per,
    blk_per,
    to_per,
    fouls_per_40
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    usage = "Usage", 
    AST_TO_ratio = "AST/TO",
    EFG_per = "EFG%",
    TS_per = "TS%",
    dr_per = "DREB%",
    or_per = "OREB%",
    stl_per = "STL%",
    blk_per = "BLK%",
    to_per = "TO%",
    fouls_per_40 = "Fouls/40"
  ) |> 
  gt_theme_ncaa()
```

## Player Impact Metrics (`{r} player_stats_total |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(GP)` Games)
```{r}
#| echo: false
player_stats_total |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  mutate(
    porpagatu = round(porpagatu, 2), 
    d_porpagatu = round(d_porpagatu, 2),
    total_prpg = round(total_prpg, 2),
    OBPM_torvik = round(OBPM_torvik, 2),
    DBPM_torvik = round(DBPM_torvik, 2),
    BPM_torvik = round(BPM_torvik, 2)
  ) |> 
  select(
    porpagatu, 
    d_porpagatu,
    total_prpg,
    OBPM_torvik,
    DBPM_torvik,
    BPM_torvik
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    porpagatu = "Off. PRPG",
    d_porpagatu = "Def. PRPG",
    total_prpg = "Total PRPG",
    OBPM_torvik = "Off. BPM",
    DBPM_torvik = "Def. BPM",
    BPM_torvik = "BPM"
  ) |> 
  gt_theme_ncaa()
```

## Player Impact Metrics vs Top 100 Teams (`{r} player_stats_vs_tournament |> filter(athlete_display_name == params$player, team_location == params$team) |> pull(games_played)` Games)
```{r}
#| echo: false
player_stats_vs_tournament |> 
  filter(
    athlete_display_name == params$player,
    team_location == params$team
  ) |> 
  mutate(
    porpagatu = round(porpagatu, 2), 
    d_porpagatu = round(d_porpagatu, 2),
    total_prpg = round(total_prpg, 2),
    OBPM_torvik = round(OBPM_torvik, 2),
    DBPM_torvik = round(DBPM_torvik, 2),
    BPM_torvik = round(BPM_torvik, 2)
  ) |> 
  select(
    porpagatu, 
    d_porpagatu,
    total_prpg,
    OBPM_torvik,
    DBPM_torvik,
    BPM_torvik
  ) |> # turn into a nice gt table
  gt() |> 
  # format column names
  cols_label(
    porpagatu = "Off. PRPG",
    d_porpagatu = "Def. PRPG",
    total_prpg = "Total PRPG",
    OBPM_torvik = "Off. BPM",
    DBPM_torvik = "Def. BPM",
    BPM_torvik = "BPM"
  ) |> 
  gt_theme_ncaa()
```
